\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-27 OaklandSubmission/intro.tex
kerschbaum

\subsubsection*{Related Work}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
  and some have also developed tools that allow writing such combinations
  (e.g. \cite{bogdanov,lone,tasty}). Kerschbaum et al.~\cite{autoS}
  even provide a scheme to automatically select optimal protocols
  for sub-compuations. However, as Demmler et al.~\cite{aby} note, due
  to high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. Additionally, these prior works neither have a
developer-friendly language, nor do they formalize their type system
and operational semantics, and show them to be consistent.
We provide a detailed survey of related work in \sectionref{related}.

>>>>

\subsubsection*{Related Work}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
and some have also developed tools that allow writing such
combinations (e.g. \cite{bogdanov,lone,tasty}). However, as Demmler et
al.~\cite{aby} note, due
 to high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. Additionally, these prior works neither have
a developer-friendly language, nor do they formalize their type
system and operational semantics, and show them to be
consistent. Kerschbaum et al.~\cite{autoS}
provide a scheme to automatically select optimal protocols
for sub-compuations, but they consider a toy language consisting only
of arithmetic expressions. We provide a detailed survey of related
work in \sectionref{related}.
